Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-10 pnas/Towards.tex
no message

%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
%\begin{corollary}
%	%Let $K=1$ and $\sigma > 0$ be fixed.
%	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
%\end{corollary}

%This can be added to an arxiv version of the paper	
From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
\begin{corollary}
	%Let $K=1$ and $\sigma > 0$ be fixed.
	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
	\begin{itemize}
		\item Either the signal $x$ is generic; or
		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
	\end{itemize}
\end{corollary}
%
%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}

>>>>

From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
\begin{corollary}
	%Let $K=1$ and $\sigma > 0$ be fixed.
	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
\end{corollary}
%
%%This can be added to an arxiv version of the paper	
%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
%\begin{corollary}
%	%Let $K=1$ and $\sigma > 0$ be fixed.
%	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
%	\begin{itemize}
%		\item Either the signal $x$ is generic; or
%		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
%	\end{itemize}
%\end{corollary}
%
%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
